---
output: github_document
---
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active) [![license](https://img.shields.io/badge/license-MIT + file LICENSE-lightgrey.svg)](http://choosealicense.com/)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# gephi

This is a simple package to export files into a csv format that 
gephi can understand.


I've found the need to convert tidygraph/igraph objects into a node and edge csv, to visualize in gephi quite often. 
This should be trivial, but gephi is a bit particular and wants specific column names. 

## What does the package do?
Writes igraph files to csv format that gephi likes.
Really? Gephi reads csv files just fine! 
Sure but it wants the columns in a particular order and named Source, Target etc. Let's not do this by hand everytime: AUTOMATE THE BORING STUFF! 


## Installation

Install this developmental version with:

```{r,eval=FALSE} 
# install.packages("devtools")
devtools::install_github("RMHogervorst/gephi")
```


## Example

* igraph to csv
* tidygraph to csv
* dataframe to csv

Writing out an igraph file to csv:

```{r example}
library(gephi)
library(igraph)
V(graphexample)
E(graphexample)
gephi_write_edges(graphexample, "edges.csv")
```

Technically an tidygraph object is also an igraph object
so the writing will work the same.

```{r}
library(gephi)
library(tidygraph)
graphexample
```

More specifically if you want to modify and 
visualize a subset of your
graph in gephi:

```{r}
graphexample %>% 
    activate(nodes) %>% 
    filter(color == "blue") %>% 
    activate(edges) %>% 
    mutate(dongle = "dingle") %>% 
    gephi_write_edges("edges_subset.csv") %>% 
    print()
```

But is is also possible to write a set of edges when there is
no graph object, just a dataframe.

```{r}
data.frame(
    start = c(1,2,3,4,5,6,7),
    finish = c(2,4,4,7,2,1,3),
    weight = c(1,1,1,2,6,1,1)
) %>% 
    print() %>% 
    gephi_write_edges_from_df(path = "edges2.csv")
```



```{r cleaning up afterwards}
file.remove("edges.csv")
file.remove("edges2.csv")
file.remove("edges_subset.csv")
```


